---
title: "4th Floor Fantasy Draft 2026"
author: "Evan Oman"
date: "September 6, 2026"
output:
  html_document:
    toc: true
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
options(width=100)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This document looks at how our league handled the 2026 Fantasy Football Draft. We have drafted without cheatsheets since 2016, so every manager has to arrive with their own plan. That setup leads to big swings in pick quality, which makes the draft a fun case study each year.

Throughout the analysis I use the ESPN Superflex PPR rankings as a proxy for player value. The list is far from perfect, but it serves as a consistent yardstick for comparing draft decisions.

Source code and data live at https://github.com/EvanOman/FantasyFootball, and you can reach me via http://www.evanoman.com.

Let the fun begin!

## Data Preparation

The draft data uses the confirmed eight-team snake order and includes all 128 picks. Fauxgendaz's round-11 Etienne entry is treated as Travis Etienne Jr. (ESPN rank 45), based on Evan's recollection that the higher-ranked Etienne was drafted. The supplied table contains only one Etienne entry.

Load the data:

```{r}
draftData <- read.csv("./data/Draft2026.csv", stringsAsFactors = FALSE)

# Align column names with the rest of the workflow
names(draftData)[names(draftData) == "OverallPick"] <- "PickNumber"
names(draftData)[names(draftData) == "Position"] <- "Pos"
names(draftData)[names(draftData) == "FantasyTeam"] <- "Drafter"

print.data.frame(head(draftData), row.names = FALSE)
```

The file is already in the tall format we need, so we can move straight to the rankings.

For 2026 we use the September 2 ESPN PPR Superflex Top 300 from [Board Calls](https://evanoman.com/board-calls/). ESPN's sheet assumes 10 teams; our draft has eight. Rankings provide the same comparison as last year's report.

```{r}
rankings <- read.csv("./data/espn_superflex_ppr_2026.csv", stringsAsFactors = FALSE)

# Keep positional labels from the rankings distinct from the draft data
names(rankings)[names(rankings) == "Pos"] <- "RankPos"

# Read player as string, not factor
rankings$Player <- as.character(rankings$Player)

print.data.frame(head(rankings, n=10), row.names=FALSE)
```

This dataset is also tall, so no additional reshaping is necessary. With both tables ready we join `draftData` and `rankings` on `Player`. Because this is a left join, every draft pick is retained even if the player falls outside the top 300. Names and positions are checked before export. The four players or defenses absent from the Top 300 use `nrow(rankings) + 1` (301) as a comparison value, following the previous report; 301 is not an observed ESPN rank.

```{r}
library("dplyr")
library("DT")

# Join rankings data with draft data
joinedData <- left_join(draftData, rankings, by="Player")

# Some players will not have a  ranking, give these players a worst ranking + 1
joinedData$Rank[is.na(joinedData$Rank)] <- nrow(rankings) + 1

print.data.frame(head(joinedData, n=10), row.names=FALSE)
```

The result contains every pick, its pick number, and the ESPN ranking. From here we can measure pick quality using the difference between those two numbers.

```{r}
joinedData$RankDiff <- joinedData$Rank - joinedData$PickNumber

print.data.frame(head(joinedData, n=10), row.names=FALSE)
```

With the data prepped we can move on to summarizing the draft.

## Figures and Results

A natural starting point is the average difference between pick number and rank for each drafter. We calculate that with `aggregate`.

```{r}
avgDiffs <- aggregate(RankDiff ~ Drafter, joinedData, FUN=mean)

# Order factor by worst draft to best
avgDiffs <- within(avgDiffs, Drafter <- factor(Drafter, levels=avgDiffs[order(avgDiffs$RankDiff), "Drafter"]))

# Order dataframe by worst draft to best
avgDiffs <- avgDiffs[order(avgDiffs$RankDiff, decreasing = FALSE),]

print.data.frame(avgDiffs, row.names=FALSE)
```

From this table we learn that `r bd <- avgDiffs[which.min(avgDiffs$RankDiff),]; bd$Drafter` had the lowest average rank difference (his average pick was `r bestDiff <- bd$RankDiff; abs(bestDiff)` slots `r if (bestDiff < 0) "later than" else "earlier than"` the ESPN rank) while `r wd <- avgDiffs[which.max(avgDiffs$RankDiff),]; wd$Drafter` struggled the most (averaging `r worstDiff <- wd$RankDiff; abs(worstDiff)` spots `r if (worstDiff < 0) "later than" else "earlier than"` the ESPN rank). The bar chart below gives the same view at a glance.

```{r}
library(ggplot2)
ggplot(avgDiffs, aes(x=Drafter, y=RankDiff)) + geom_bar(stat = "identity") + ylab("Mean Difference Between Pick # and Ranking")
```

Kickers and defenses affect the averages, so I also check the results after removing those positions:

```{r}
noKorDst <- joinedData[!(joinedData$Pos %in% c("DST", "K")), ]

avgDiffs2 <- aggregate(RankDiff ~ Drafter, noKorDst, FUN=mean)

# Order factor by worst draft to best
avgDiffs2 <- within(avgDiffs2, Drafter <- factor(Drafter, levels=avgDiffs[order(avgDiffs$RankDiff), "Drafter"]))

# Order dataframe by worst draft to best
avgDiffs2 <- avgDiffs2[order(avgDiffs2$RankDiff, decreasing = FALSE),]

print.data.frame(avgDiffs2, row.names=FALSE)
```
Next I look at positional trends to see which spots were over- or undervalued.

```{r}
posDiffs <- aggregate(RankDiff ~ Pos, joinedData, FUN=mean)

posDiffs <- within(posDiffs, Pos <- factor(Pos, levels=posDiffs[order(posDiffs$RankDiff), "Pos"]))

# Order dataframe by worst draft to best
posDiffs <- posDiffs[order(posDiffs$RankDiff, decreasing = FALSE),]

print.data.frame(posDiffs, row.names=FALSE)

ggplot(posDiffs, aes(x=Pos, y=RankDiff)) + geom_bar(stat = "identity") + ylab("Mean Difference Between Pick # and Ranking")
```

The chart shows that `r bpd <- posDiffs[which.min(posDiffs$RankDiff),]; bestDiff <- bpd$RankDiff; bpd$Pos` were `r if (bestDiff < 0) "under" else "over"` valued by `r abs(bestDiff)` picks on average, while `r wpd <- posDiffs[which.max(posDiffs$RankDiff),]; worstDiff <- wpd$RankDiff; wpd$Pos` were `r if (worstDiff < 0) "under" else "over"` valued by `r abs(worstDiff)` picks.

The next two plots chart `Pick #` versus `Rank` with a diagonal "break-even" line. Points below the line were bargains; points above were reaches. The first plot highlights drafters and the second highlights positions.

```{r}
# Scatter colored by drafter
ggplot(joinedData, aes(x=PickNumber,y=Rank)) + geom_point(aes(color=Drafter)) + geom_abline() + xlab("Pick #")
```

```{r}
# Scatter colored by position
ggplot(joinedData, aes(x=PickNumber,y=Rank)) + geom_point(aes(color=Pos)) + geom_abline() + xlab("Pick #")
```

The largest gaps show which picks differed most from ESPN's rankings.

Finally, I look at the round-by-round swings for each drafter. In the figure below, anything below the dashed line is a win and anything above is a reach.

```{r}
# Scatter colored by position, faceted by drafter
ggplot(joinedData, aes(x=Round, y=RankDiff)) + geom_line() + facet_wrap(~Drafter, ncol=2) + geom_hline(yintercept = 0, linetype=2) + geom_point(aes(color=Pos)) + ylab("Difference Between Pick # and Ranking")
```

## Conclusion
Here are the key takeaways using all positions and the same rank-difference measure as before:

- **Best Draft:** `r bd <- avgDiffs[which.min(avgDiffs$RankDiff),]; bd$Drafter` (avg pick `r bestDiff <- bd$RankDiff; abs(bestDiff)` positions `r if (bestDiff < 0) "later than" else "earlier than"` ESPN rank)
- **Worst Draft:** `r wd <- avgDiffs[which.max(avgDiffs$RankDiff),]; wd$Drafter` (avg pick `r worstDiff <- wd$RankDiff; abs(worstDiff)` positions `r if (worstDiff < 0) "later than" else "earlier than"` ESPN rank)
- **Best Pick:** Drafter: `r p <- joinedData[which.min(joinedData$RankDiff),]; p$Drafter`, Round: `r p$Round`, Player: `r p$Player`,  Rank Difference: `r p$RankDiff`
- **Worst Pick:** Drafter: `r p <- joinedData[which.max(joinedData$RankDiff),]; p$Drafter`, Round: `r p$Round`, Player: `r p$Player`,  Rank Difference: `r p$RankDiff`

## Pick Ledger

```{r}
rawTable <- joinedData[order(joinedData$PickNumber), c("PickNumber", "Round", "Drafter", "Player", "Rank", "RankDiff")]

datatable(
  rawTable,
  colnames = c("Pick #", "Round", "Team", "Player", "ESPN Rank", "Rank Diff"),
  filter = "top",
  options = list(pageLength = 25, autoWidth = TRUE)
)
```
